The ``encrypt-then-MAC'' transformations

### 2024-06-29 faster-fo-transform/etm-transform/main.tex
Trying a new appriach

>>>>

\section{Plaintext Awareness: a new approach}
A new approach I can think of is as follows:

\begin{enumerate}
    \item prove that $\etm$ transformed schemes are plaintext aware
    \item prove that if a scheme is plaintext aware, then it is OW-CCA2
\end{enumerate}

Both steps are non-trivial, though the second step can be heavily borrowed from \cite{bellare1998relations}.

\subsection{$\etm$ is plaintext aware}

\subsection{Plaintext-awareness implies OW-CCA2}
